---
title: "Gender Name Bias (N=750)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(ggbrace)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(ggplot2)
library(grid)
library(extrafont)
library(readxl)
library(nnet)
library(systemfit)
library(aod)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}

```

\newpage

## Read Data

```{r echo=TRUE}
#write.csv(qual_data, "raw_data.csv")
## Pull directly from Qualtrics API
qual_data <- fetch_survey(surveyID='SV_3xQRyUFmFz29fXU',
                   label = T,
                   convert = F,
                   start_date = "2025-03-07",
                   force_request = T)

# Read the Excel file
professors_data <- read_excel("Academic -- dataset.xlsx")
```


```{r}
# Create a lookup table for citizenship based on First_name
citizenship_lookup <- professors_data %>%
  mutate(region = case_when(
    Citizenship %in% c("China", "South_Korea", "Thailand") ~ "Eastern",
    Citizenship %in% c("Germany", "Italy", "United_Kingdom") ~ "Western",
    TRUE ~ NA_character_
  )) %>%
  select(First_name, region)

# Define categories based on first names
women <- professors_data$First_name[professors_data$Gender == "Female"]  
admin <- professors_data$First_name[professors_data$title_admon == 1]  
sciences <- professors_data$First_name[professors_data$Field_category == "Sciences"]  
public_univ <- professors_data$First_name[professors_data$`Private/public` == "public"]  

# failed attention check

failed_d0 <- qual_data |> 
  filter(is.na(`Q32_Page Submit`) | is.na(workerId))

# left early

left_early_d0 <- qual_data |> 
  filter(!is.na(`Q32_Page Submit`), !is.na(workerId), is.na(`choice7`))

# Create the analysis dataset
d0 <- qual_data |> 
    filter(!is.na(`choice7`), !is.na(workerId), Finished==1) |> 
    mutate(
    gender_feedback = as.numeric(grepl("% are women", feedbackItem1) |
                  grepl("% are women", feedbackItem2) |
                  grepl("% are women", feedbackItem3)),
    admin_shown = as.numeric(grepl("% hold an administrative position", feedbackItem1) |
                  grepl("% hold an administrative position", feedbackItem2) |
                  grepl("% hold an administrative position", feedbackItem3)),
    sciences_shown = as.numeric(grepl("% work in the sciences", feedbackItem1) |
                grepl("% work in the sciences", feedbackItem2) |
                grepl("% work in the sciences", feedbackItem3)),
    public_shown = as.numeric(grepl("% earned their PhDs at public universities", feedbackItem1) |
                 grepl("% earned their PhDs at public universities", feedbackItem2) |
                 grepl("% earned their PhDs at public universities", feedbackItem3)),
    female_pick = case_when(`choice7` %in% women ~ 1,
                           TRUE ~ 0),
    admin_pick = case_when(`choice7` %in% admin ~ 1,
                           TRUE ~ 0),
    sciences_pick = case_when(`choice7` %in% sciences ~ 1,
                           TRUE ~ 0),
    public_pick = case_when(`choice7` %in% public_univ ~ 1,
                           TRUE ~ 0),
    citizenship = sapply(`choice7`, function(x) 
      citizenship_lookup$region[citizenship_lookup$First_name == x]),
    gender_region = case_when(
      female_pick == 1 & citizenship == "Eastern" ~ "Female_Eastern",
      female_pick == 1 & citizenship == "Western" ~ "Female_Western",
      female_pick == 0 & citizenship == "Eastern" ~ "Male_Eastern",
      female_pick == 0 & citizenship == "Western" ~ "Male_Western"),
    female_eastern = (female_pick == 1 & citizenship == "Eastern") * 1,
    female_western = (female_pick == 1 & citizenship == "Western") * 1,
    gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
    race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
    base_gender = rowSums(across(`choice1`:`choice6`, ~ . %in% women))) |> 
  select(gender_feedback:citizenship, gender, base_gender, `choice1`:`choice7`,gender_region:female_western, race, age, gender_code, race_code)
# write.csv(qual_data, "raw_data.csv", row.names = FALSE)
# write.csv(d0, "study1_clean.csv", row.names = FALSE)
```

\newpage

## Demographics

```{r results='markup'}
## Failed Attention Check

cat('Failed Attention Check Participants:', nrow(failed_d0), '\n')
    
## Participants that were randomly assigned but didn't click final DV Attention Check

cat('Participants without DV but condition assignment:', nrow(left_early_d0), '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

cat('Mean (age): ', round(mean(d0$age), 2))
cat('SD (age): ',round(sd(d0$age), 2))

```

\newpage

## Primary Analysis

## SUR, followed by Wald Test


```{r echo=FALSE, results='markup'}
options(scipen = 999)
robust_summary(lm(female_eastern ~ gender_feedback, data=d0))
robust_summary(lm(female_western ~ gender_feedback, data=d0))
# Seemingly unrelated regression
sur_formula <- list(
  eastern = female_eastern ~ gender_feedback,
  western = female_western ~ gender_feedback
)

sur_model <- systemfit(sur_formula, method="SUR", data=d0)
summary(sur_model)$coefficients

# Wald test to compare coefficients
# Testing whether the effect of gender_feedback is different for Eastern vs Western women
linearHypothesis(sur_model, 
                 "eastern_gender_feedback - western_gender_feedback = 0", test = "Chisq")

# Get robust coefficients and standard errors
robust_summary_no_controls <- coeftest(sur_model, vcov = vcovHC(sur_model, type = "HC1"))
print(robust_summary_no_controls)
```

\newpage

## Robustness Tests

### Model with demographic controls

```{r echo=FALSE, results='markup'}
robust_summary(lm(female_eastern ~ gender_feedback + gender_code + race_code + age, data=d0))
robust_summary(lm(female_western ~ gender_feedback + gender_code + race_code + age, data=d0))
sur_formula_demographics <- list(
  eastern = female_eastern ~ gender_feedback + gender_code + race_code + age,
  western = female_western ~ gender_feedback + gender_code + race_code + age
)

sur_model_demographics <- systemfit(sur_formula_demographics, method="SUR", data=d0)
linearHypothesis(sur_model_demographics, 
                 "eastern_gender_feedback - western_gender_feedback = 0")

summary(sur_model_demographics)

```

\newpage

### Handling dropouts - Assuming male scholar selection

```{r echo=FALSE, results='markup'}

d0_male <- d0
dropout_data <- left_early_d0 %>%
  mutate(female_eastern = 0,
         female_western = 0)
d0_combined_male <- bind_rows(d0, dropout_data)

sur_model_male <- systemfit(sur_formula, method="SUR", data=d0_combined_male)
#summary(sur_model_male)
linearHypothesis(sur_model_male, 
                 "eastern_gender_feedback - western_gender_feedback = 0")


```


\newpage

### Handling dropouts - Assuming female Eastern scholar selection

```{r echo=FALSE, results='markup'}

d0_eastern <- d0
dropout_data_eastern <- left_early_d0 %>%
  mutate(female_eastern = 1,
         female_western = 0)
d0_combined_eastern <- bind_rows(d0, dropout_data_eastern)

sur_model_eastern <- systemfit(sur_formula, method="SUR", data=d0_combined_eastern)
#summary(sur_model_eastern)
linearHypothesis(sur_model_eastern, 
                 "eastern_gender_feedback - western_gender_feedback = 0")

```

\newpage


### Handling dropouts - Assuming female Western scholar selection

```{r echo=FALSE, results='markup'}

d0_western <- d0
dropout_data_western <- left_early_d0 %>%
  mutate(female_eastern = 0,
         female_western = 1)
d0_combined_western <- bind_rows(d0, dropout_data_western)

sur_model_western <- systemfit(sur_formula, method="SUR", data=d0_combined_western)
#summary(sur_model_western)
linearHypothesis(sur_model_western, 
                 "eastern_gender_feedback - western_gender_feedback = 0")

```

\newpage

### Robustness Summary table


```{r echo=FALSE, results='markup'}
# Create a summary table of results
results_summary <- data.frame(
  Model = c("Base Model", "With Demographics", "Dropouts as Male", 
            "Dropouts as Eastern Female", "Dropouts as Western Female"),
  Eastern_Coef = c(coef(sur_model)[2], 
                   coef(sur_model_demographics)[2],
                   coef(sur_model_male)[2],
                   coef(sur_model_eastern)[2],
                   coef(sur_model_western)[2]),
  Western_Coef = c(coef(sur_model)[4],
                   coef(sur_model_demographics)[4],
                   coef(sur_model_male)[4],
                   coef(sur_model_eastern)[4],
                   coef(sur_model_western)[4]),
  Wald_p_value = c(linearHypothesis(sur_model, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_demographics, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_male, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_eastern, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_western, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2])
)

# Print the results table
kable(results_summary, digits = 3,
      caption = "Robustness Check Results across Different Model Specifications")

```


\newpage

## Figure

```{r}
# Load the package
library(ggbrace)

# Create data for Eastern women
eastern_data <- d0 |> 
  group_by(gender_feedback) |> 
  summarise(
    freq = mean(female_pick * (citizenship == "Eastern")),
    se = (sd(female_pick * (citizenship == "Eastern")) / sqrt(n()))
  ) |>
  mutate(
    Region = "Eastern",
    Feedback = if_else(gender_feedback == 1, "Feedback provided", "No feedback")
  )

# Create data for Western women
western_data <- d0 |> 
  group_by(gender_feedback) |> 
  summarise(
    freq = mean(female_pick * (citizenship == "Western")),
    se = (sd(female_pick * (citizenship == "Western")) / sqrt(n()))
  ) |>
  mutate(
    Region = "Western",
    Feedback = if_else(gender_feedback == 1, "Feedback provided", "No feedback")
  )

# Combine data for plotting
plot_data <- bind_rows(eastern_data, western_data) |>
  mutate(
    Region = factor(Region, levels = c("Eastern", "Western"),
                   labels = c("Eastern Women", "Western Women")),
    Feedback = factor(Feedback, levels = c("No feedback", "Feedback provided"))
  )

# Calculate the differences (deltas) for annotations
delta_data <- plot_data %>%
  select(Region, Feedback, freq) %>%
  pivot_wider(names_from = Feedback, values_from = freq) %>%
  mutate(delta = (`Feedback provided` - `No feedback`) * 100)

delta_eastern_val <- delta_data$delta[delta_data$Region == "Eastern Women"]
delta_western_val <- delta_data$delta[delta_data$Region == "Western Women"]

# Get bar heights for brace positioning
eastern_freqs <- plot_data$freq[plot_data$Region == "Eastern Women"][order(plot_data$Feedback[plot_data$Region == "Eastern Women"])] * 100
western_freqs <- plot_data$freq[plot_data$Region == "Western Women"][order(plot_data$Feedback[plot_data$Region == "Western Women"])] * 100

# Define explicit x-coordinates to place braces to the right of the bars
x_brace_east <- 1.55
x_text_east  <- 1.60
x_brace_west <- 2.55
x_text_west  <- 2.60

# Create specific data frames for each brace
brace_east_df <- data.frame(x = c(x_brace_east, x_brace_east), y = eastern_freqs)
brace_west_df <- data.frame(x = c(x_brace_west, x_brace_west), y = western_freqs)


# Create the final, comprehensive plot
p1 <- ggplot(plot_data, aes(x = Region, y = freq * 100, fill = Feedback)) +
  geom_bar(stat = "identity", 
           position = position_dodge(width = 0.9), 
           width = 0.8) +
  geom_text(aes(label = sprintf("%.1f%%", freq * 100)),
            position = position_dodge(width = 0.9),
            vjust = 3.5,
            color = "white",
            size = 6,
            fontface = "bold") +
  geom_errorbar(aes(ymin = (freq - se) * 100, 
                    ymax = (freq + se) * 100),
                position = position_dodge(width = 0.9),
                width = 0.2) +
  
  # 1. The original horizontal significance lines
  annotate("segment", x = 0.75, xend = 1.25, y = 15, yend = 15) +
  annotate("text", x = 1, y = 16.5, label = "n.s.", size = 4.5) +
  
  annotate("segment", x = 1.75, xend = 2.25, y = 25, yend = 25) +
  annotate("text", x = 2, y = 26.5, label = "***", size = 5.5) +

  # 2. The independent vertical braces, correctly positioned and directed
  stat_brace(data = brace_east_df, aes(x = x, y = y), inherit.aes = FALSE,
             rotate = 270, width = 0.1) +
  annotate("text", x = x_text_east, y = mean(eastern_freqs), label = sprintf("Δ = %.1f%%", delta_eastern_val),
           size = 6.5, fontface = "italic", hjust = 0) +
  
  stat_brace(data = brace_west_df, aes(x = x, y = y), inherit.aes = FALSE,
             rotate = 270, width = 0.1) +
  annotate("text", x = x_text_west, y = mean(western_freqs), label = sprintf("Δ = %.1f%%", delta_western_val),
           size = 6.5, fontface = "italic", hjust = 0) +

  # Styling
  scale_fill_manual(values = c(
    "No feedback" = "#011F5B",     
    "Feedback provided" = "#990000" 
  )) +
  scale_y_continuous(limits = c(0, 42), expand = c(0, 0)) +
  labs(y = "% of Final Academics Selected who were Women") +
  theme_bw() +
  theme(
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.line = element_line(color = "black"),
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    legend.position = "top",
    legend.title = element_blank(),
    axis.title.x = element_blank(),
    axis.text = element_text(size = 19, color = "black"),
    axis.title.y = element_text(size = 19, color = "black", margin = margin(r = 10)),
    legend.text = element_text(size = 16)
  )

# Print the plot
p1
ggsave('study3.png', p1, width = 9, height = 7)

```