---
title: "Gender Name Bias (N=750)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  pdf_document: 
    toc: yes
    toc_depth: 2
    fig_caption: true
header-includes:
  \renewcommand{\contentsname}{Items}
   \usepackage{fvextra}
   \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	results = "hide"
)
library(dplyr)
library(lmtest)
library(sandwich)
library(systemfit)
library(car)
library(broom)
library(qualtRics)
library(knitr)
library(rmarkdown)
library(ggplot2)
library(grid)
library(extrafont)
library(readxl)
library(nnet)
library(systemfit)
library(aod)
library(ggplot2)
library(dplyr)
library(tidyverse)
```

```{r include=FALSE}
if ( (!is.null(knitr::current_input()))) {
  if (("pdf_document" ==
                rmarkdown::all_output_formats(knitr::current_input())[1])) {
      stargazer_type <- "latex"
  }
} else {
  stargazer_type <- "text"
}

robust_summary <- function(model) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting original model summary
    model_summary <- summary(model)

    # Updating standard errors, t-values, and p-values in the coefficients table
    model_summary$coefficients[, "Std. Error"] <- robust_se
    model_summary$coefficients[, "t value"] <- model_summary$coefficients[, "Estimate"] / robust_se
    model_summary$coefficients[, "Pr(>|t|)"] <- 2 * pt(-abs(model_summary$coefficients[, "t value"]), df = model_summary$df[2], lower.tail = TRUE)

    return(model_summary)
}
robust_confint <- function(model, level = 0.95) {
    # Calculating robust standard errors
    robust_se <- sqrt(diag(vcovHC(model, type = "HC3")))

    # Getting the coefficients
    est <- coef(model)

    # Calculating the critical value for the t-distribution
    alpha <- 1 - level
    t_crit <- qt(1 - alpha / 2, df = df.residual(model))

    # Calculating the confidence intervals
    lower <- est - t_crit * robust_se
    upper <- est + t_crit * robust_se

    # Combining into a matrix
    confint <- cbind(lower, upper)
    rownames(confint) <- names(est)
    colnames(confint) <- c("2.5 %", "97.5 %")

    return(confint)
}

```

\newpage

## Read Data

```{r echo=TRUE}
#write.csv(qual_data, "raw_data.csv")
## Pull directly from Qualtrics API
qual_data <- fetch_survey(surveyID='SV_8whRwyQHrL0PdD8',
                   label = T,
                   convert = F,
                   start_date = "2024-11-22",
                   force_request = T)

# Read the Excel file
professors_data <- read_excel("Nameselect_1022_humancheck.xlsx")
```


```{r}
# Create a lookup table for citizenship based on First_name
citizenship_lookup <- professors_data %>%
  mutate(region = case_when(
    Citizenship %in% c("China", "South_Korea", "Thailand") ~ "Eastern",
    Citizenship %in% c("Germany", "Italy", "United_Kingdom") ~ "Western",
    TRUE ~ NA_character_
  )) %>%
  select(First_name, region)

# Define categories based on first names
women <- professors_data$First_name[professors_data$Gender == "Female"]  
admin <- professors_data$First_name[professors_data$Binary_HaveRole == "Yes"]  
sciences <- professors_data$First_name[professors_data$Field_category == "Sciences"]  
public_univ <- professors_data$First_name[professors_data$`Private/public` == "public"]  

# failed attention check

failed_d0 <- qual_data |> 
  filter(is.na(`Q32_Page Submit`) | is.na(workerId))

# left early

left_early_d0 <- qual_data |> 
  filter(!is.na(`Q32_Page Submit`), !is.na(workerId), is.na(`choice-7`))

# Create the analysis dataset
d0 <- qual_data |> 
    filter(!is.na(`choice-7`), !is.na(workerId), Finished==1) |> 
    mutate(
    gender_feedback = as.numeric(grepl("% are women", feedbackItem1) |
                  grepl("% are women", feedbackItem2) |
                  grepl("% are women", feedbackItem3)),
    admin_shown = as.numeric(grepl("% hold an administrative position", feedbackItem1) |
                  grepl("% hold an administrative position", feedbackItem2) |
                  grepl("% hold an administrative position", feedbackItem3)),
    sciences_shown = as.numeric(grepl("% work in the Sciences", feedbackItem1) |
                grepl("% work in the Sciences", feedbackItem2) |
                grepl("% work in the Sciences", feedbackItem3)),
    public_shown = as.numeric(grepl("% earned their PhDs at public universities", feedbackItem1) |
                 grepl("% earned their PhDs at public universities", feedbackItem2) |
                 grepl("% earned their PhDs at public universities", feedbackItem3)),
    female_pick = case_when(`choice-7` %in% women ~ 1,
                           TRUE ~ 0),
    admin_pick = case_when(`choice-7` %in% admin ~ 1,
                           TRUE ~ 0),
    sciences_pick = case_when(`choice-7` %in% sciences ~ 1,
                           TRUE ~ 0),
    public_pick = case_when(`choice-7` %in% public_univ ~ 1,
                           TRUE ~ 0),
    citizenship = sapply(`choice-7`, function(x) 
      citizenship_lookup$region[citizenship_lookup$First_name == x]),
    gender_region = case_when(
      female_pick == 1 & citizenship == "Eastern" ~ "Female_Eastern",
      female_pick == 1 & citizenship == "Western" ~ "Female_Western",
      female_pick == 0 & citizenship == "Eastern" ~ "Male_Eastern",
      female_pick == 0 & citizenship == "Western" ~ "Male_Western"),
    female_eastern = (female_pick == 1 & citizenship == "Eastern") * 1,
    female_western = (female_pick == 1 & citizenship == "Western") * 1,
    gender_code = case_when(gender=="Man" ~ 1, TRUE ~ 0),
    race_code = case_when(race=="White / Caucasian" ~ 1, TRUE ~ 0),
    base_gender = rowSums(across(`choice-1`:`choice-6`, ~ . %in% women))) |> 
  select(gender_feedback:citizenship, gender, base_gender, `choice-1`:`choice-7`,gender_region:female_western, race, age, gender_code, race_code)
```

\newpage

## Demographics

```{r results='markup'}
## Failed Attention Check

cat('Failed Attention Check Participants:', nrow(failed_d0), '\n')
    
## Participants that were randomly assigned but didn't click final DV Attention Check

cat('Participants without DV but condition assignment:', nrow(left_early_d0), '\n')

## Gender

gender_percentages <- round(prop.table(table(d0$gender)) * 100, 2)

gender_df <- data.frame(
  Percentage = gender_percentages,
  gender = names(gender_percentages)
)[1:2]

colnames(gender_df) <- c("Percentage", "gender")

print(gender_df)


## Race

race_percentages <- round(prop.table(table(d0$race)) * 100, 2)

race_df <- data.frame(
  Percentage = race_percentages,
  Race = names(race_percentages)
)[1:2]

colnames(race_df) <- c("Percentage", "Race")

print(race_df)

## Age

cat('Mean (age): ', round(mean(d0$age), 2))
cat('SD (age): ',round(sd(d0$age), 2))

```

\newpage

## Primary Analysis

## SUR, followed by Wald Test


```{r echo=FALSE, results='markup'}
options(scipen = 999)
# Seemingly unrelated regression
sur_formula <- list(
  eastern = female_eastern ~ gender_feedback*race_code,
  western = female_western ~ gender_feedback*race_code
)

summary(lm(female_eastern ~ gender_feedback*race_code, data=d0))
summary(lm(female_western ~ gender_feedback*race_code, data=d0))

sur_model <- systemfit(sur_formula, method="SUR", data=d0)
summary(sur_model)$coefficients

# Wald test to compare coefficients
# Testing whether the effect of gender_feedback is different for Eastern vs Western women
linearHypothesis(sur_model, 
                 "eastern_gender_feedback - western_gender_feedback = 0")


```

\newpage

## Robustness Tests

### Model with demographic controls

```{r echo=FALSE, results='markup'}
sur_formula_demographics <- list(
  eastern = female_eastern ~ gender_feedback + gender_code + race_code + age,
  western = female_western ~ gender_feedback + gender_code + race_code + age
)

sur_model_demographics <- systemfit(sur_formula_demographics, method="SUR", data=d0)
#summary(sur_model_demographics)
linearHypothesis(sur_model_demographics, 
                 "eastern_gender_feedback - western_gender_feedback = 0")


```

\newpage

### Handling dropouts - Assuming male scholar selection

```{r echo=FALSE, results='markup'}

d0_male <- d0
dropout_data <- left_early_d0 %>%
  mutate(female_eastern = 0,
         female_western = 0)
d0_combined_male <- bind_rows(d0, dropout_data)

sur_model_male <- systemfit(sur_formula, method="SUR", data=d0_combined_male)
#summary(sur_model_male)
linearHypothesis(sur_model_male, 
                 "eastern_gender_feedback - western_gender_feedback = 0")


```


\newpage

### Handling dropouts - Assuming female Eastern scholar selection

```{r echo=FALSE, results='markup'}

d0_eastern <- d0
dropout_data_eastern <- left_early_d0 %>%
  mutate(female_eastern = 1,
         female_western = 0)
d0_combined_eastern <- bind_rows(d0, dropout_data_eastern)

sur_model_eastern <- systemfit(sur_formula, method="SUR", data=d0_combined_eastern)
#summary(sur_model_eastern)
linearHypothesis(sur_model_eastern, 
                 "eastern_gender_feedback - western_gender_feedback = 0")

```

\newpage


### Handling dropouts - Assuming female Western scholar selection

```{r echo=FALSE, results='markup'}

d0_western <- d0
dropout_data_western <- left_early_d0 %>%
  mutate(female_eastern = 0,
         female_western = 1)
d0_combined_western <- bind_rows(d0, dropout_data_western)

sur_model_western <- systemfit(sur_formula, method="SUR", data=d0_combined_western)
#summary(sur_model_western)
linearHypothesis(sur_model_western, 
                 "eastern_gender_feedback - western_gender_feedback = 0")

```

\newpage

### Robustness Summary table


```{r echo=FALSE, results='markup'}
# Create a summary table of results
results_summary <- data.frame(
  Model = c("Base Model", "With Demographics", "Dropouts as Male", 
            "Dropouts as Eastern Female", "Dropouts as Western Female"),
  Eastern_Coef = c(coef(sur_model)[2], 
                   coef(sur_model_demographics)[2],
                   coef(sur_model_male)[2],
                   coef(sur_model_eastern)[2],
                   coef(sur_model_western)[2]),
  Western_Coef = c(coef(sur_model)[4],
                   coef(sur_model_demographics)[4],
                   coef(sur_model_male)[4],
                   coef(sur_model_eastern)[4],
                   coef(sur_model_western)[4]),
  Wald_p_value = c(linearHypothesis(sur_model, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_demographics, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_male, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_eastern, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2],
                   linearHypothesis(sur_model_western, 
                    "eastern_gender_feedback - western_gender_feedback = 0")$"Pr(>F)"[2])
)

# Print the results table
kable(results_summary, digits = 3,
      caption = "Robustness Check Results across Different Model Specifications")

```

```{r}
# Set seed for reproducibility
set.seed(42)
n <- 2000

# Create a dataframe
data_sim <- data.frame(
  participant_id = 1:n,
  western_participant = rep(c(1, 0), each = n/2),
  gender_feedback = rep(rep(c(0, 1), each = n/4), 2)
)

# Function to assign probabilities
assign_probabilities <- function(western_participant, gender_feedback) {
  if (gender_feedback == 0) {
    # Control group: Equal probabilities for both regions
    return(c(WF = 0.1, EF = 0.10))
  } else {
    # Treatment group
    if (western_participant == 1) {
      # Western participants
      return(c(WF = 0.50, EF = 0.25))  # Larger increase for WF
    } else {
      # Eastern participants
      return(c(WF = 0.50, EF = 0.32))  # Larger increase for EF
    }
  }
}

# Simulate choices
data_sim$western_female <- NA
data_sim$eastern_female <- NA

for (i in 1:nrow(data_sim)) {
  probs <- assign_probabilities(data_sim$western_participant[i], data_sim$gender_feedback[i])
  data_sim$western_female[i] <- rbinom(1, 1, probs["WF"])
  data_sim$eastern_female[i] <- rbinom(1, 1, probs["EF"])
}

# Load necessary libraries
library(systemfit)
library(car)

# Convert variables to factors
data_sim$gender_feedback <- as.factor(data_sim$gender_feedback)
data_sim$western_participant <- as.factor(data_sim$western_participant)

### Modeling for RQ1

# Define equations without interaction terms
eq1_rq1 <- western_female ~ gender_feedback + western_participant
eq2_rq1 <- eastern_female ~ gender_feedback + western_participant

# Combine into a system
system_rq1 <- list(westernEq = eq1_rq1, easternEq = eq2_rq1)

# Fit the SUR model
sur_model_rq1 <- systemfit(system_rq1, method = "SUR", data = data_sim)

# Summary of the model for RQ1
summary(sur_model_rq1)

# Testing hypothesis for RQ1
wald_test_rq1 <- linearHypothesis(sur_model_rq1, "westernEq_gender_feedback1 - easternEq_gender_feedback1 = 0")
print("Wald Test for RQ1:")
print(wald_test_rq1)

### Modeling for RQ2

# Define equations with interaction terms
eq1_rq2 <- western_female ~ gender_feedback * western_participant
eq2_rq2 <- eastern_female ~ gender_feedback * western_participant

# Combine into a system
system_rq2 <- list(westernEq = eq1_rq2, easternEq = eq2_rq2)

# Fit the SUR model
sur_model_rq2 <- systemfit(system_rq2, method = "SUR", data = data_sim)

# Summary of the model for RQ2
summary(sur_model_rq2)

# Testing hypothesis for RQ2
interaction_test_rq2 <- linearHypothesis(sur_model_rq2, 
                                         "westernEq_gender_feedback1:western_participant1 - easternEq_gender_feedback1:western_participant1 = 0")
print("Wald Test for RQ2:")
print(interaction_test_rq2)


```